Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-23 bdcloud_paper/latex/paper.tex
Edited MSM equations

Markov Models are used to model the customer's purchasing behavior for each item category.  Each state $X_n$ corresponds to an item in that category. The customer's buying habits are determined by the transition probabilities (Eq.~\ref{eq:transition_probabilities}).  The transition probabilities depend on three types of parameters: loopback weight $w_l$ indicating the probability of purchasing the same item again, weight $w_f$ of a particular field $f$, and the weight $w_{f,s}$ when two items $x$ and $y$ have the same value for the field $f$.

\begin{align} \label{eq:transition_probabilities}
Pr(X_{n+1}&=x|X_n) = \nonumber \\
& \left\{ 
  \begin{array}{l l}
   (1.0 - w_l) W^{-1} \sum_f w_f w_{f,s}(x, y)  & \quad \text{if $x \neq X_n$}\\
   w_l & \quad \text{if $x = X_n$}
  \end{array} \right.
\end{align}

\textcolor{red}{todo}

@@

\textcolor{red}{todo}

\begin{equation*}
W = \sum_i \sum_{j \neq i} \sum_f w_f w_{f,s}(i, j)
\end{equation*}

The weights $w_l$, $w_f$, and $w_{f, s}$ are chosen randomly for each customer.

\textcolor{red}{description. min, max}

\begin{align} \label{eq:item-weights}
&w_l \sim N(\mu, \sigma^2) \nonumber \\
&w_f \sim N(\mu, \sigma^2) \nonumber \\
&w_{f, s} \sim N(\mu, \sigma^2)
\end{align}

>>>>

Markov Models are used to model the customer's purchasing behavior for each item category.  Each state $X_n$ corresponds to an item in that category. The customer's buying habits are determined by the transition probabilities:

\begin{align}
Pr(X_{n+1}&=x|X_n=y) = \nonumber \\
& \left\{ 
  \begin{array}{l l}
   (1.0 - p_l) \, Pr(x,y)  & \quad \text{if $x \neq y$}\\
   p_l & \quad \text{if $x = y$}
  \end{array} \right.
\end{align}

where $w_l$ is the loopback probability, giving the probability of choosing the same item $y$ again. The function $Pr(x,y)$ gives the probability of choosing the item $x$ given that the previous item was $y$:

\begin{equation*}
Pr(x,y) = \frac{\sum_f w_f w_{f,s}(x, y)}{\sum_{j \neq x} \sum_f w_f w_{f,s}(x, j)}
\end{equation*}

where $w_f$ is the weight of a particular field $f$.   The pair of items $x$ and $y$ are weighted  according to the equality of the values for each field:

@@

The weights $w_l$, $w_f$, and $w_{f, s}$ are chosen randomly for each customer:

\begin{align*}
&w_l \sim N(\mu, \sigma^2) \\
&w_f \sim N(\mu, \sigma^2) \\
&w_{f, s} \sim N(\mu, \sigma^2)
\end{align*}

If the weights are greater than 1, they are rounded down to 1.  Likese, if the weights are less than 0, they are rounded up to 0.
